%-------------------------
% Resume in Latex
% Author : Shubhi Rani
% License : MIT
%https://www.overleaf.com/articles/resume-shubhi-rani-apr-2019/fhxzrkcmjzjp
%------------------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Zachary Dempsey}} & Email : \href{mailto:zacdempsey3@gmail.com}{zacdempsey3@gmail.com}\\
  Mobile : +61 450 175 673 \\
  %\href{https://github.com/dempz}{Github: https://github.com/dempz} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Western Australia}{Perth, Western Australia}
      {Bachelor of Philosophy with First Class Honours in Mathematics \& Statistics}{Feb 2018\textendash Oct 2022}
      
	   {\small Mathematics \& Statistics and Finance \linebreak\vspace{0mm} \textit{WAM: 92.481; GPA: 6.963}}
	   %\newline
	   %{\scriptsize \textit{Courses: Static/Dynamic Optimisation, Numerical Analysis, Dynamical Systems, Nonlinear Dynamics and Chaos, Complex Systems}}
	    
	    
    \resumeSubheading
      {University of Manchester}{Manchester, United Kingdom}
      {Exchange Programme;  GPA: 82.2/First Class}{Aug 2019\textendash Feb 2020}
      
    \resumeSubheading
      {Mount Lawley Senior High School}{Perth, Western Australia}
      {ATAR: 99.70}{Nov 2017}
  \resumeSubHeadingListEnd
  
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
    {The Kids Research Institute Australia (formerly Telethon Kids Institute)}{Perth, Western Australia}
    {Biostatistician}{Mar 2023\textendash Present}
    \resumeItemListStart
        \resumeItem{}{Provide expert consultation to research fellows, students and research teams \textemdash both internal and external to the Institute \textemdash on study design, data management, and analysis across epidemiological, clinical, health, and laboratory settings.}
        \resumeItem{}{Collaborate with diverse research teams in fields such as neonatal emergency and critical care, dentistry, psychology, population health, and social sciences.}
        \resumeItem{}{Helped establish and contribute to the Institute's biostatistics blog and and Institute ``Hacky Hour'', helping educate and give one-on-one support to researchers with statistical analysis and data management and cleaning techniques.}
        \resumeItem{}{Extensive experience in cleaning, wrangling and linking large, complex datasets, including government administrative data.}
        \resumeItem{}{Present and communicate complex analytical findings using a reproducible research framework, leveraging Git and Quarto markdown.}
        \resumeItem{}{Creator and maintainer of tailor-made R package for consistent reporting and analytical frameworks for working with multiple analysts across a complex multidisciplinary research project.}
        %\resumeItem{}{Operating in a consultative capacity to support students, researchers/research teams both internal and external to the Institute. Chiefly, consultations revolve around study design, data collection and management, and analysis across epidemiological, clinical and laboratory settings.}
        %\resumeItem{}{Engaged by a breadth of research teams and interests, spanning neonatal care, dentistry, psychology, population health and social sciences.}
        %\resumeItem{}{Extensive expertise with cleaning/wrangling, linking large and complex analytical data sets.}
        %\resumeItem{}{Experience using/cleaning large and complex data files spanning from research teams to linked government administrative data.}
        %\resumeItem{}{Written communication skills -- reporting of analytical results. Convey the output of robust statistical models in an easy to follow way.}
        %\resumeItem{}{Contribute to the Institute's biostatistics blog}
        %\resumeItem{}{Contribute to a reproducible research framework, using git and reporting using Rmarkdown and Quarto .}
        %\resumeItem{}{Contribute to the reintroduction of the Institute's Hacky Hour}
        %\resumeItem{}{Create and manage custom-made R package for large datra project.}
        %\resumeItem{}{Expanded quantitative toolbox with robust statistical methods to apply to complex data sets of various nature. Experience using hierarchical statistical models to account for complex nesting structure in a data set.}
        %\resumeItem{}{AI presentation? Using AI in statistical workflows?}
    \resumeItemListEnd
    
    \resumeSubheading
    {AssetOwl Technologies}{Perth, Western Australia}
    {Data Analyst/Research and Development Consultant}{Jul 2021\textendash Jul 2022}
    \resumeItemListStart
        \resumeItem{}{As the sole research and development consultant I focussed on using creative data analysis techniques to expand the Company's product offerings consistent with its growth strategy. Leveraging the visual inspection data collected by the Company's real estate visual inspection tool, I proposed two independent avenues for future expansion. A thorough R\&D report was delivered; it detailed the current state of the industry, relevant existing applications in other industries (e.g. engineering) and the mathematical/computational techniques used for analysis.}
        \resumeItem{}{Liaised between management, the engineering and finance teams to identify the unique contributions to the industry's state of knowledge/available commercial products. By concisely communicating each of the novel projects to AusIndustry, the Company was able to apply for the best possible research and development subsidies.}
        \resumeItem{}{Able to communicate research progress, technical details and recommendations accurately and concisely in both verbal and in written report form to managers and the Company's Board of Directors.}
    \resumeItemListEnd
      
%    \resumeSubheading
%		{Giant Cannington}{Perth, Western Australia}
%		{Salesperson/Assistant Bicycle Mechanic}{Jul 2020\textendash Feb 2022}
%		\resumeItemListStart
%        \resumeItem{}{Bicycle salesperson, ranging from entry- to high-level competition road and mountain bicycles, to suit each customer's requirements.}
%        \resumeItem{}{Competent in diagnosing problems, making recommendations on faults, and servicing all types of bicycles.}
%        \resumeItem{}{Experience in coordinating with supplier representatives and state-wide warehouse distribution center for Giant Bicycles Australia on new products, developments, and special-order items.}
%        \resumeItem{}{Experience in operating point-of-sales system, including cash management, and the opening and closing of the till.}
%        \resumeItem{}{Given stock taking responsibilities, consistent with store policies, utilizing the inventory function of the store’s point-of-sales system.}
%        \resumeItem{}{Able to actively and enthusiastically participate and coordinate in a team-working environment. Ongoing responsibilities included the training of junior staff members in sales, technical and general retail skills.}
%    \resumeItemListEnd

    \resumeSubheading
    {University of Western Australia}{Perth, Western Australia}
    {STAT1520 Laboratory Facilitator}{Jun 2021\textendash Nov 2021}
    \resumeItemListStart
    \resumeItem{}{Facilitator of laboratories for STAT1520: Economics and Business Statistics for the School of Mathematics and Statistics. The unit establishes a foundational understanding in discrete and continuous random variables, sampling, ANOVA and univariate and multivariate regression techninques.}
    \resumeItem{}{Coordinated multiple in-person classes each week, coaching students of a non-science background through a range of fundamental and extension questions aimed to develop their skills in fundamental statistical analysis techniques.}
    \resumeItem{}{Marker of assessment items (tests, exams).}
    \resumeItemListEnd
    
    \resumeSubheading
    {University of Western Australia}{Perth, Western Australia}
    {Research Assistant, The Complex Systems Group, Department of Mathematics and Statistics}{Jul 2020\textendash Nov 2020}
    \resumeItemListStart
    \resumeItem{}{Investigated how complex network methods can be leveraged for nonlinear time series analysis.}
    \resumeItem{}{Developed methods using Julia for detecting critical transitions in coupled dynamical systems.}
    \resumeItem{}{Learned how to concisely communicate findings and articulate questions to academic staff.}
    \resumeItemListEnd
    
    \resumeSubheading
    {UWA Student Managed Investment Fund (SMIF)}{Perth, Western Australia}
    {Equity Analyst}{Jun 2018\textendash Aug 2020}
    \resumeItemListStart
    \resumeItem{}{Conducted qualitative and quantitative research on ASX-listed companies in accordance with the fund’s philosophies to prepare and pitch recommendations to professional fund managers at Viburnum Funds.}
    \resumeItem{}{Experience researching within agribusiness, insurance construction, litigation funding and retail industries.}
    \resumeItem{}{Conducted qualitative analysis of competitive landscapes, industries and business, revenue and cost figures, acquisition trends, contractual terms, and regulatory risk.}
    \resumeItem{}{Input in the construction of company valuation models like discounted cash flow and comparable companies/transactions based on qualitative research findings.}
    \resumeItemListEnd
    
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Academic Projects}
\resumeSubHeadingListStart
\resumeSubheading
    {Honours Dissertation}{Perth, Western Australia}
    {Title: Ordinal Partition Network-of-Networks for Paleoclimate Analysis}{Feb 2022\textendash Oct 2022}
    \resumeItemListStart
    \resumeItem{}{Developed a novel technique for analysing coupled nonlinear systems by combining previously independent concepts from complex systems theory. In doing so, we successfully built a powerful, computationally efficient and robust (with respect to artificially noise-corrupted data) tool for analysing the complex interactions between multidimensional nonlinear time series.}
    \resumeItem{}{The method was successful in identifying sensitive temporal coupling transitions between simulated and real-world (paleoclimate) nonlinear systems. A monsoon strength proxy was extracted from a paleoclimate reanalysis dataset to analyse the couplings between East Asian-Indonesian-Australian Summer Monsoon regions. Our method shows marked transition points in regional monsoon coupling strengths coincident with established local climate events (volcanic eruptions, droughts).}
    \resumeItem{}{All background theory, data structures and results were presented in a 30-minute seminar to a non-specialist mathematical audience.}
    \resumeItem{}{Project entirely development and implemented using base functionalities of Python.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%--------PUBLICATIONS------------
\section{Publications}
\begin{itemize}
    \item Divakara N, Dempsey Z, Saraswati C, Garssen J, Silva D, Keelan JA, Christophersen CT, Cooper MN, Prescott SL, Palmer DJ, Verhasselt V, Macchiaverni P. (2024) Effect of maternal prebiotic supplementation on human milk immunological composition: Insights from the SYMBA study. \textit{Pediatric Allergy and Immunology} DOI: \url{https://doi.org/10.1111/pai.14226}
    \item \textsc{[in review]} Ong CSY, Rodgers J, Cooper MN, Dempsey Z, Eaton R, Haines K, Kuzminski R, Magiati I, Maybery MT, Uljarević M, Wray J, Whitehouse AJO, Alvares GA. (2024) Targeting Intolerance of Uncertainty in Young Children Diagnosed with Autism: A Randomized Controlled Trial of a Parent-Mediated Group Intervention.
\end{itemize}

%--------PROGRAMMING SKILLS------------
\section{Skills/Interests}
	\resumeSubHeadingListStart
	\resumeSubItem{Programming Languages: }{Python, Julia, R}
	\resumeSubItem{Tools: }{Matlab, Wolfram Mathematica, RStudio, Rmarkdown, Quarto, Git, Microsoft Office (Word, Powerpoint, Excel)}
	\resumeSubItem{Courses: }{Linear programming, calculus of variations, optimal control, numerical analysis, dynamical systems, nonlinear dynamics and chaos, complex systems analysis}
	\resumeSubItem{Interests: }{Road cycling, vintage vehicle restoration, data visualisation, biostatistics}
\resumeSubHeadingListEnd

%-----------Awards-----------------
\section{Honours and Awards}
\begin{description}[font=$\bullet$]
\item {Wesfarmers Business Development Prize (Jul 2021)} 
\item {Frank Gamblen Scholarship in Mathematics (Sep 2019)}
\item {Nicholas Searcy Prize in Multivariable Calculus (Mar 2019)}
\item {Ronald and Irene Searcy Prize in Mathematical Methods and Theory (Mar 2019)}
\item {Mount Lawley Senior High School WACE Year 12 ATAR DUX (Nov 2017)}
\end{description}
%-------------------------------------------
\end{document}
