%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}

\moderncvstyle{classic}                            
\moderncvcolor{black}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.80]{geometry}

% personal data
\name{Zachary Dempsey}{}
\email{zacdempsey3@gmail.com}
\phone[mobile]{+61 450 175 673}               
%\address{Village, City - State, Country}


\begin{document}

\recipient{To}{Telethon Kids Institute \\
               Perth Children's Hospital\\
               15 Hospital Avenue\\
               Nedlands WA 6009
               }
\date{\today}
\opening{\textbf{Application for the role of Biostatistician}}
\closing{Yours sincerely, \vspace{-1em}}


%\enclosure[Enclosed (Marksheets/Certificates)]{
%              \\ 1. SSLC (Admit/MarkSheet/Certificate)
%                 \hspace{0.0em} 5. GATE (2016) \hspace{2em} 9. Identity-Proof (Voter-Id)\\
%                 2. Diploma (MarkSheet/Certificate)
%                 \hspace{1.8em} 6. SLET (2021) \hspace{1.9em} 10. Resume\\        
%                 3. B.Tech (MarkSheet/Certificate)
%                 \hspace{2.3em} 7. UGC-NET (2022) \hspace{-0.1em} \\
%                 4. M.Tech (MarkSheet/Certificate)
%                 \hspace{2.1em} 8. Caste Certificate \\
%                 }
\makelettertitle

Dear Sir/Madam,
\vspace{1em}
\\
I graduated in October 2022 from the University of Western Australia with a Bachelor of Philosophy with First Class Honours in Mathematics and Statistics, specialising in the Applied Mathematics stream. Additionally, in my undergraduate years, I completed a second major in finance. These fields, the challenging logical problems they entail, and challenging analytical problems in general, serve to captivate and intrigue me. My study of these disciplines has infused both my verbal and non-verbal problem-solving skills with creativity, insight, and expertise.
\vspace{1em}
\\
Throughout my undergraduate and Honours I have enthusiastically engaged with and excelled in my studies. My Honours thesis contributed a novel technique for analysing multivariate nonlinear time series, using both simulated and paleoclimate reanalysis data. In addition to receiving the highest collective Honours score in my cohort, I received some of the highest grades in the Honours coursework units covering optimisation (92), numerical analysis (91) and dynamical systems (95). My undergraduate studies in mathematics rewarded me with the Frank Gamblen Scholarship for Mathematics as well as prizes for both Multivariable Calculus (99) and Mathematical Methods and Theory (96). My achievements demonstrate my long-standing commitment and passion for the field of mathematics and statistics.  
\vspace{1em}
\\
From my study and research, I have found that working with complex real-world datasets, naturally, contain anomalies not encountered in theoretical or simulated data. Overcoming the difficulties of working with these datasets is crucial in accurately and efficiently performing data analysis. From the units I have completed throughout my degree, I have worked with data ranging from finance and economics, to physical, biological and mechanical applications. As a more specific example, my Honours thesis analysed paleoclimate data\textendash where past states of the earth's climate is reconstructed for a time \emph{before} direct instrumental measurement was possible. The complex data structure necessary to store paleoclimate data was something I had not worked with before, and was an additional hurdle I overcame to successfully analyse the data. This is to say that, despite my limited experience working with an extensive health database, I am confident in my ability to adapt to work with and analyse any \emph{new} data types that may present themselves in this role.
\vspace{1em}
\\
My programming abilities have been developed independently and driven by a continual passion for learning. For my thesis, I independently researched and learned to code in Python. This ultimately enabled me to utilise only Python's base functionalities for all required mathematical, statistical and plotting tasks. This is also the case for learning to code using Julia, necessitated by my further study in advanced dynamical systems during my Honours year. While my present understanding of using R is somewhat limited (driven thus far purely on my personal interest), its syntactic similarity to Python gives me confidence in quickly and thoroughly grasping its functionalities for the role going forward.
\vspace{1em}
\\
Oral presentations, seminars and talks have been something I have often struggled with growing up. Both my previous work experience and time at university, however, have granted me opportunities to hone these communication skills and build this confidence. In my previous role as a research and development consultant at AssetOwl Technologies, I was responsible for researching future expansion avenues by analysing the company's visual inspection data. To convey these ideas, I composed a thorough report to distribute to my managers in addition to giving a presentation to the Company's Board of Directors. At university, I was a laboratory facilitator for STAT1520, where I would take a class of approximately 30 students through each week's content and practice questions. Finally, as the final assessment in my final year of university, I was required to give a 30-minute seminar on my thesis topic to a non-specialist audience; conveying the motivation, construction and results of my research. For this role as biostatistician, I am eager for the additional opportunities I will have to communicate mathematical and statistical ideas and improve further.
\vspace{1em}
\\
Outside of work and study, I commit myself to, and take great satisfaction from, a road cycling schedule regimen. In my remaining time, I enjoy working on the restoration of my 1971 Land Rover Series IIA, which I have almost completely overhauled over the last two years. I have always believed in having a well-rounded skill set where I am able to work with both the abstract and concrete, which can be applied to a range of situations and environments.
%\vspace{1em}
%\\
%Collecting, collating and analysing data using the comprehensive quantitative toolbox of the modern sciences is vital for our understanding of the modern, complex world we live in. In particular reference to
\vspace{0.5cm}

\makeletterclosing

\end{document}
